
\section{Associated Attractor Results}

In Section \ref{ANsec}, a pullback absorbing neighbourhood was
shown to guarantee the existence of a pullback attractor within a
pullback absorbing neighbourhood. However, confirmation in a
likewise manner for forward attractors cannot be achieved.

The only available approach to locate a forward attractor in a similar fashion
is to locate a pullback attractor via an absorbing neighbourhood and determine
its uniformity. The property of uniformity implies completeness of attraction
(and hence forward convergence). This is formalised in the following lemmas
which are an extension of Lemmas \ref{upscslem}, \ref{ufscslem},
\ref{upascaslem}, \ref{ufascaslem}.

\begin{lemma}
\label{uattlem}
If pullback attraction to a pullback attractor $\hat{A}$ is uniform, then
$\hat{A}$ is a complete attractor.
\end{lemma}
\begin{prf}
Pullback attraction to $\hat{A}$ is uniform. That is, given an $\e > 0$,
there exists a $\hat{\delta} = \{\delta\}$ only, and a $T=T(\e)$ such that for
every $p \in P$ and for all $t > T(\e)$
\[ H^*(\Phi_{(t,\theta_{-t}p)}(\mathcal{N}_{\delta}(A(\theta_{-t}p)),A(p))
                        < \e. \]
We make the substitution $\theta_t p$ for $p$ in the above
equation, noting that the bounds $\delta$ and $T(\e)$ are
independent of $p$ and thus still valid. Then for some $\e > 0$,
every $p \in P$ and $t > T(\e)$,
\[ H^*(\Phi_{(t,p)}(\mathcal{N}_{\delta}(A(p)),A(\theta_t p)) < \e. \]
Thus $\hat{A}$ satisfies the property of forwards convergence and as a
result is a {\em complete attractor}.
\end{prf}

\begin{lemma}
If forward attraction to a forward attractor $\hat{A}$ is uniform, then
$\hat{A}$ is a complete attractor.
\end{lemma}
\begin{prf}
The proof for the second Lemma follows similarly.
\end{prf}

\endinput
