
\begin{thebibliography}{99}
\bibitem{Ap74}
  Tom Apostol,
  \emph{Mathematical Analysis}
  Addison-Wesley Publishing Company, 1974.
\bibitem{Ar98}
  L.Arnold,
  \emph{Random Dynamical Systems},
  Springer-Verlag, New York Inc., 1998.
\bibitem{ArPl90}
  D.Arrowsmith \& C.Place,
  \emph{An introduction to Dynamical Systems},
  Cambridge University Press, Cambridge, 1990.
\bibitem{BhSz67}
  N.P. Bhatia \& G.P. Szeg\"{o},
  \emph{Dynamical Systems: Stability theory and application},
  Lecture Notes in Mathematics, No.37, Springer, Berlin, 1967.
\bibitem{CaPihttp}
  Julyan Cartwright \& Oreste Piro,
  \emph{The Dynamics of Runge-Kutta Methods},
  School of Mathematical Sciences,
  University of London,
  `http://lec.ugr.es/~julyan/papers/rkpaper/root.html'.
\bibitem{ChKlSc98}
  D.Cheban, P.Kloeden \& B.Schmalfuss,
  \emph{Pullback Attractors in Dissipative Nonautonomous Differential Equations
               under Discretization},
  In Proc. of EQUADIFF 99,  1024-1029, Berllin,
  World Scientific, Singapore,  2000.
\bibitem{ChKlSc00}
  D.Cheban, P.Kloeden \& B.Schmalfuss,
  \emph{The Relationship Between Pullback, Forwards and Global Attractors of
                  Nonautonomous Dynamical Systems},
  Nonlinear Dynamics and Systems Theory, 2000.

\bibitem{ChKlSc01}
  D.Cheban, Peter Kloeden and B. Schmalfuss,
  \emph{Pullback Attractors in Dissipative Nonautonomous Differential Equations
       Under Discretization} , J. Dynamical Systems and Differential Equations 13, 185-213, 2001.

\bibitem{CrFlDe97}
  H. Crauel, F. Flandoli \& A. Debussche,
  \emph{Random Attractors},
  Journal of Dynamics and Differential Equations,
  Vol. 9, No. 2, 1997.
\bibitem{CrFl94}
  H. Crauel \& F. Flandoli,
  \emph{Attractors for Random Dynamical Systems},
  Probability Theory and Related Fields 100,  1095-1113, 1994.
\bibitem{Fa90}
  K.Falconer,
  \emph{Fractal Geometry. Mathematical Foundations and Applications},
  John Wiley and Sons,
  Chichester, 1990.
\bibitem{FlSc96}
  F. Flandoli \& B.Schmalfuss,
  \emph{Random Attractors of the 3D Navier Stokes Equation with Multiplicative
  White Noise},
  Stochastics and Stochastics Reports 59,  21-45, 1996.
\bibitem{FS95}
  Fang Shuhong,
  \emph{Global Attractor for General Nonautonomous Dynamical Systems},
  Nonlinear World. 2,  191-216, 1995.
\bibitem{JoRi82}
  L.Johnson \& D.Riess,
  \emph{Numerical Analysis},
  Addison-Wesley Publishing Company,
  Philippines, 1982.
\bibitem{Kl98}
  Peter Kloeden,
  \emph{Construction of a Lyapunov Function for Cocycle Attractors in
  Non-Autonomous Difference Equations},
  Electronic Journal of Differential Equations,
  Conference 05,  91-102, 2000.
\bibitem{KlKo99}
  P.Kloeden \& V.Kozyakin,
  \emph{The Inflation of Attractors and their Discretization: The Autonomous
              Case},
  Nonlinear Analysis,  333-343, TMA 40, 2000.
\bibitem{KlKo00}
  P.Kloeden \& V.Kozyakin,
  \emph{The Inflation of Nonautonomous Systems and their Pullback Attractors},
  Izvestiya of hte Russian Academy of Natural Sciences, Series MMMIU, 4, No.
                 1-2, 2000.
\bibitem{KlKo01}
  P.Kloeden \& V.Kozyakin,
  \emph{Uniform Nonautonomous Attractors under Discretization},
  DANSE-Preprint 36/2000, Discrete Continuous Dynamical Systems (to appear).
\bibitem{KlLo86}
  Peter Kloeden \& J. Lorenz,
  \emph{Stable Attracting Sets in Dynamical Systems and their
  One-Step Discretisations},
  SIAM J. Numer. Anal. 23,  986-995, 1986.
\bibitem{KlSc95}
  Peter Kloeden \& B. Schmalfuss,
  \emph{Nonautonomous Systems, Cocycle Attractors and Varable Time-Step
          Discretization},
  Annals of Numerical Mathematics.
\bibitem{KlSc96}
  Peter Kloeden \& B. Schmalfuss,
  \emph{Lyapunov Functions and Attractors Under Variable Time-Step
  Discretisation},
  Discrete and Continuous Dynamical Systems 2, 163-172, 1996.
\bibitem{PkSt97}
  Peter Kloeden \& Daniel Stonier,
  \emph{Cocycle Attractors in Nonautonomous Perturbed Differential
  Equations},
  Dyanmics of Discrete, Continuous and Impulsive Systems, \textbf{4},
              211-226, 1998.
\bibitem{LaLe67}
  Joseph La Salle \& Solomon Lefschetz,
  \emph{Stability by Liapunov's Direct Method},
  Academic Press, New York, 1967.
\bibitem{Mo62}
  R.Moore,
  \emph{Introduction to Differential Equations},
  Allyn and Bacon, Boston, 1962.
\bibitem{Pe91}
  Lawrence Perko,
  \emph{Differential Equations and Dynamical Systems},
  Springer-Verlag, New York Inc., 1991.
\bibitem{Re72}
  Albert Reinstein,
  \emph{Introduction to Ordinary Differential Equations},
  Academic Press, 1972.
\bibitem{RoHaLa77}
  N.Rouche, P.Habets \& M.Laloy,
  \emph{Stability Theory by Liapunov's Direct Method},
  Springer-Verlag, New York, 1977.
\bibitem{Sc92}
  B.Schmalfuss,
  \emph{The Stochastic Attractor of the Stochastic Lorenz System},
  Nonlinear Dynamics: Attractor Approximation and Global Behaviour, Proc. ISAM
  92, TU Dresden,  185-192, 1992.
\bibitem{Sc99}
  B.Schmalfuss,
  \emph{Attractors for the Nonautonomous Dynamical Systems},
  In Proc. of EQUADIFF 99, Berlin,
  World Scientific, Singapore,  1024-1029,   2000.
\bibitem{Se67}
  G.R.Sell,
  \emph{Nonautonomous Differential Equations and Topological Dynamics I,
  II},
  Trans. Amer. Math. Soc. 127,  241-283, 1967.
\bibitem{Se71}
  G.R.Sell,
  \emph{Lectures on Topological Dynamics and Differential Equations},
  Van Nostrand-Reinbold, London, 1971.
\bibitem{Sk91}
  J.Skowronski,
  \emph{Control of Nonlinear Mechanical Systems},
  Plenum Press, New York, 1991.
\bibitem{St73}
  H.J.Stetter,
  \emph{Analysis of Discretisation Methods for Ordinary Differential
  Equations},
  Springer-Verlag, Heidelberg, 1973.
\bibitem{St94}
  Andrew Stuart,
  \emph{Analysis of Numerical Dynamical Systems},
  Acta Numerica 2, 1994.
\bibitem{StHu96}
  Andrew Stuart \& A.R. Humphries,
  \emph{Numerical Analysis and Dynamical Systems},
  Cambridge University Press, Cambridge, 1996.
\bibitem{St01a}
  Daniel Stonier,
  \emph{Pullback Stability and Attraction for Non-Autonomus Dynamical Systems},
  Journal of Nonlinear Science(submitted).
\bibitem{St01b}
  Daniel Stonier,
  \emph{Discretisation of Asymptotically Stable Non-Autonomous Dynamical
       Systems},
  Journal of Nonlinear Science(submitted).
\bibitem{St01c}
  Daniel Stonier,
  \emph{Duality of Attraction},
  Journal of Nonlinear Science(submitted).
\bibitem{Te88}
  R. Teman,
  \emph{Infinite-Dimensional Dynamical Systems in Mechanics and
  Physics},
  Springer-Verlag, Heidelberg, 1988.
\bibitem{Vi92}
  M.I. Vishik,
  \emph{Asymptotic Behaviour of Solutions of Evolution Equations},
  Cambridge University Press, Cambridge, 1992.
\bibitem{Yo59}
  T.Yoshizawa,
  \emph{Liapunov's Function and Boundedness of Solutions},
  Funkcialaj Ekvacioj, 2, 1959.
\bibitem{Yo66}
  T.Yoshizawa,
  \emph{Stability Theory By Liapunov's Second Method},
  Mathematical Society of Japan, 1966.
\end{thebibliography}

\endinput
